Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-16 summary.Rmd
forgot to add minor addition

In the second example, we applied Algorithm 2 to the British MPs Twitter 
network \cite{greene2013producing}, the Political Blogs network and the DBLP network. For this data analysis, we subsetted the data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
networks. Our methods underperformed compared to modularity maximization, although performance is comparable for the British MPs and DBLP networks.

>>>>

In the second example, we applied Algorithm 2 to the British MPs Twitter 
network \cite{greene2013producing}, the Political Blogs network and the DBLP n
etwork. For this data analysis, we subsetted the data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
networks. Our methods underperformed compared to modularity maximization, 
although performance is comparable for the British MPs and DBLP networks. In 
addition, Algorithm 2's runtime is much lower than that of modularity 
maximization.
